### 2013-04-09 exam6/2.tex
Rubric for problem 1.

\ifrubric\else
\newpage
[Here is some more space for the previous problem.]
\fi

@@

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage
\newpage
\end{problem}

>>>>

\ifrubric

\begin{solution}
\begin{verbatim}
// [1pt]
interface BST<X> extends Iterable<X> {
    // Insert given element into this BST.
    BST<X> insert(X x);
}

// [optional]
abstract class ABST<X> implements BST<X> {
    Comparator<X> c;
    ABST(Comparator<X> c) {
        this.c = c;
    }
}

// [1pt: fields, constructor, parameterized type]
class Leaf<X> extends ABST<X> {
    Leaf(Comparator<X> c) {
        super(c);
    }

    // [1pt]
    public BST<X> insert(X x) {
        return new Node<X>(this.c, x, this, this);
    }
}

// [2pt: fields, constructor, parameterized type]
class Node<X> extends ABST<X> {
    X x;
    BST<X> left;
    BST<X> right;
    Node(Comparator<X> c, X x, BST<X> left, BST<X> right) {
        super(c);
        this.x = x;
        this.left = left;
        this.right = right;
    }

    // [3pt]
    public BST<X> insert(X x) {
        return (this.c.compare(x, this.x) < 0)
        ? new Node<X>(this.c, this.x, this.left.insert(x), this.right)
        : new Node<X>(this.c, this.x, this.left, this.right.insert(x));
        }
    }
}

// [2pt: tests]
\end{verbatim}
\end{solution}

\else
\newpage
[Here is some more space for the previous problem.]
\fi

@@

\ifrubric
\begin{solution}
\begin{verbatim}
// [5pt]
class Sort {
    <X> ArrayList<X> treeSort(Comparator<X> c, Iterable<X> elems) {
        BST<X> bst = new Leaf<X>(c);
        ArrayList<X> ls = new ArrayList<X>();
        for (X x : elems) bst = bst.insert(x);
        for (X x : bst)   ls.add(x);
        return ls;
    }
}

// [2pt]
class LessThan implements Comparator<Integer> {
    public int compare(Integer x, Integer y) {
        return x - y;
    }
}

// [3pt]
class Examples {
    void testTreeSort(Tester t) {
        Sort s = new Sort();
        Comparator<Integer> lt = new LessThan();
        ArrayList<Integer> elems =
            new ArrayList<Integer>(Arrays.asList(8,3,7,5));

        ArrayList<Integer> sorted =
            new ArrayList<Integer>(Arrays.asList(3,5,7,8));

        t.checkExpect(s.treeSort(lt, new ArrayList<Integer>()),
                      new ArrayList<Integer>());
        t.checkExpect(s.treeSort(lt, elems), sorted);
    }
}
\end{verbatim}
\end{solution}
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage
\newpage
\end{problem}
